%
% File acl2018.tex
%
%% Based on the style files for ACL-2017, with some changes, which were, in turn,
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2018}
\usepackage{amsmath}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{url}
\usepackage{booktabs}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Instructions for ACL 2018 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  % With development of knowledge representation, research in semantic relatedness measurement continues to make progress.
  % Most of methods for computing semantic relatedness between two words are based on
  % \emph{large corpora} and \emph{lexical databases}.
  % There are only a few of these methods utilize the knowledge graph which contains syntactic and semantic information simultaneously.
  In this paper we focus on computing semantic relatedness getting an approximation to human judgement.
  We utilize the Knowledge Graph(DBPedia) which is derived from wikipedia as the background knowledge.
  For an input pairwise word, we will get two sets of corresponding entities in DBpedia.
  Then we propose a model for extracting a subgraph which contains complete information surrounding two set of entities from DBPedia.
  Then we use a model of knowledge graph embedding to train the subgraph generating high-dimensional vector for each entity and relation. 
  Finally, we get multiple relatedness scores after a join between two set of entities.
  In order to better fit the judgement of human, we utilize a weighted strategy to combine
  multiple relatedness scores of pairwise entities.
  The experiments based on golden dataset for computing semantic relatedness show
  that our model outperform the state-of-the-art model.
\end{abstract}

\input{tex/introduction}
\input{tex/relatedwork}
\input{tex/methology}
\input{tex/experiment}
\input{tex/conclusion}

\bibliography{acl2018}
\bibliographystyle{acl_natbib}
\end{document}
